### 2020-08-21 spanish/sections/scopus-papers.tex
Create scopus-papers.tex
Update scopus-papers.tex

\cvsection{Peer-Reviewed Articles}

\cvsubsection{Scopus \& Emerging Sources Citation Index}

@@

\begin{benumerate}{7}
\item{\small Olivares, A. {\itshape et al.} (2020). New Challenges, Approaches, and Perspectives in the Study of Political Elites. {\itshape Iberoamericana, XX}(74), 229--259. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}. \\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}

>>>>

\cvsection{Publicaciones revisadas por pares}

\cvsubsection{Scopus y Emerging Sources Citation Index (ESCI)}

@@

\begin{benumerate}{7}
\item{\small Olivares, A. {\itshape et al.} (2020). Nuevos desafíos, enfoques y perspectivas para estudiar élites políticas. {\itshape Iberoamericana, XX}(74), 229--259. {\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{\textcolor{blue}{https://journals.iai.spk-berlin.de}}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{\textcolor{blue}{10.31235/osf.io/syqu4}}}\vspace{1mm}
